|

### 2023-03-09 paper/paper.Rmd
tracking data intro

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool for analyzing and deeper understanding different sports.

examples of past nfl tracking data projects

See @Baumer2023Big, @Macdonald2020Recreating, and @Kovalchik2023Player for more complete reviews on how tracking data have transformed sports analytics.

NFL, next gen stats https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/

Importance of D-linemen, pass rush (Maybe talk about role of each position, edge vs interior, defensive formation)

Previous metrics: Greg's lit review, their flaws

@@

>>>>

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.
Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

The National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016
BDB
https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/

Previous research bdb
this year: linemen
Importance of D-linemen, pass rush (Maybe talk about role of each position, edge vs interior, defensive formation)

@@

Limitations
